Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-09 doc/manuscript/manuscript.Rmd
add citation for Rocker

All data processing and analyses were performed in `r R.version.string %>% strsplit("\\(") %>% map_chr(1)`[@R] and are openly available and reproducible at https://github.com/everhartlab/sclerotinia-366/.
Of the 16 microsatellite loci genotyped, five included compound repeats, which made it challenging to accurately/confidently bin alleles into fragment sizes expected for each locus based on the described repeat motif.
Loci with compound repeats were removed for the reported statistics.
To ensure the integrity of the results we additionally processed these loci and included them in concurrent analyses.
We assessed the power of our 11 markers by generating a genotype accumulation curve in the R package *poppr* version `r packageVersion("poppr")`, looking for evidence of saturation, which would indicate that loci were sufficiently sampled to adequately represent the full set of haplotypes [@arnaud2007standardizing; @kamvar2015novel].
To avoid including isolates potentially collected from the same plant (which increases the probability of collecting sclerotia from the same point of infection more than once), data were clone-corrected on a hierarchy of Region/Source/Host/Year---meaning that duplicated genotypes were reduced to a single observation when they were collected in the same year from the same host cultivar located in the same source field (wmn or producer)---for subsequent analysis. 
We assessed haplotype diversity by calculating Stoddart and Taylor's index (*G*) [@stoddart1988genotypic], Shannon's index (*H*) [@shannon2001mathematical], Simpson's index ($\lambda$) [@simpson1949measurement], evenness ($E_5$), and the expected number of multilocus haplotypes (*eMLH*) [@heck1975explicit; @hurlbert1971nonconcept; @pielou1975ecological; @grunwald2003analysis]. 
To assess the potential for random mating, we tested for linkage disequilibrium with the index of association, $I_A$ and its standardized version, $\bar{r}_d$ using 999 permutations [@agapow2001indices; @smith1993how; @brown1980multilocus].
Both haplotype diversity and linkage disequilibrium were calculated in *poppr* [@kamvar2014poppr].

>>>>

All data processing and analyses were performed in a Rocker "verse" project container running `r R.version.string %>% strsplit("\\(") %>% map_chr(1)`[@boettiger2017introduction; @R] and are openly available and reproducible at https://github.com/everhartlab/sclerotinia-366/.
Of the 16 microsatellite loci genotyped, five included compound repeats, which made it challenging to accurately/confidently bin alleles into fragment sizes expected for each locus based on the described repeat motif.
Loci with compound repeats were removed for the reported statistics.
To ensure the integrity of the results we additionally processed these loci and included them in concurrent analyses.
We assessed the power of our 11 markers by generating a genotype accumulation curve in the R package *poppr* version `r packageVersion("poppr")`, looking for evidence of saturation, which would indicate that loci were sufficiently sampled to adequately represent the full set of haplotypes [@arnaud2007standardizing; @kamvar2015novel].
To avoid including isolates potentially collected from the same plant (which increases the probability of collecting sclerotia from the same point of infection more than once), data were clone-corrected on a hierarchy of Region/Source/Host/Year---meaning that duplicated genotypes were reduced to a single observation when they were collected in the same year from the same host cultivar located in the same source field (wmn or producer)---for subsequent analysis. 
We assessed haplotype diversity by calculating Stoddart and Taylor's index (*G*) [@stoddart1988genotypic], Shannon's index (*H*) [@shannon2001mathematical], Simpson's index ($\lambda$) [@simpson1949measurement], evenness ($E_5$), and the expected number of multilocus haplotypes (*eMLH*) [@heck1975explicit; @hurlbert1971nonconcept; @pielou1975ecological; @grunwald2003analysis]. 
To assess the potential for random mating, we tested for linkage disequilibrium with the index of association, $I_A$ and its standardized version, $\bar{r}_d$ using 999 permutations [@agapow2001indices; @smith1993how; @brown1980multilocus].
Both haplotype diversity and linkage disequilibrium were calculated in *poppr* [@kamvar2014poppr].
